Mutual Information Plots

### 2025-10-22 CMSAC_presentation/CMSAC_reveal_js.qmd
Updates

-   A limitation of mutual information is that it does not distinguish between the direction of information
-   Given equal probabilities, the information found from a ranking of $(1,2,3,4)$ is equivalent to $(4,3,2,1)$
-   Because of this, we proposed a new weighting function\
    $$ I_w(r,\hat{r}) = \sum_r \sum_{\hat{r}} w(r,\hat{r}) * p(r, \hat{r}) \log{\frac{p(r,\hat{r})}{p(r)p(\hat{r})}} $$
-   The final metric we used normalizes the results: $\frac{I_w(r,\hat{r})}{H(r,\hat{r})}$

@@

#right_html <- right_table %>% 
#  kable(format = "html", row.names = FALSE) %>% 
#  kableExtra::kable_styling(font_size = 24)
knitr::include_graphics("Top_k_Kendall.png")

@@

@@

:::::: {style="position: relative;"}
::: {.fade-out fragment-index="1"}
```{r out.width="60%", fig.show='hold', fig.align='center'}
knitr::include_graphics("boxed_tournament_comparison_plot.png")
```
:::

::: {.fragment .fade-in .fade-out fragment-index="1" fragment-index="2" style="position: absolute; top: 50%; left: 0; right: 0; transform: translateY(-50%);"}
```{r out.width="60%", fig.show='hold', fig.align='center'}
knitr::include_graphics("tournament_comparison_plot.png")
```
:::

::: {.fragment .fade-in fragment-index="2" style="position: absolute; top: 50%; left: 0; right: 0; transform: translateY(-50%);"}
```{r out.width="60%", fig.show='hold', fig.align='center'}
knitr::include_graphics("tournament_comparison_plot_close.png")
```
:::
::::::

>>>>

-   A limitation of mutual information is that it does not distinguish between the direction of information
-   Given equal probabilities, the information found from a ranking of $(1,2,3,4)$ is equivalent to $(4,3,2,1)$
-   Because of this, we proposed a new weighting function\
```{r out.width="150%", fig.show='hold', fig.align='center'}
knitr::include_graphics("Weighted_Mutual_Information_Formula.png")
```
-   The final metric we used normalizes the results: $\frac{I_w(r,\hat{r})}{H(r,\hat{r})}$

@@

#right_html <- right_table %>% 
#  kable(format = "html", row.names = FALSE) %>% 
#  kableExtra::kable_styling(font_size = 24)
#knitr::include_graphics("Top_k_Kendall.png")

@@

$$\tau_w = \frac{\sum_{i\neq j} W_{ij} \times \text{sgn}(i-j)\times \text{sgn}(R_i - R_j)}{\sum_{i,j} W_{ij} - \sum_i W_{ii}}$$

:::::: {style="position: relative; display: flex; height: 100%;"}
::: {.fragment .fade-out fragment-index="1" style="position: absolute; width: 100%;"}
```{r out.width="100%", fig.show='hold', fig.align='center'}
knitr::include_graphics("Top_2_Kendall.png")
```
:::
::: {.fragment .fade-in fragment-index="1" style="position: absolute; width: 100%;"}
```{r out.width="100%", fig.show='hold', fig.align='center'}
knitr::include_graphics("Top_3_Kendall.png")
```
:::
::::::

@@

:::::: {style="position: relative; display: flex; align-items: center; justify-content: center; height: 100%;"}
::: {.fragment .fade-out fragment-index="1" style="position: absolute; width: 100%;"}
```{r out.width="125%", fig.show='hold', fig.align='center'}
knitr::include_graphics("tournament_comparison_plot.png")
```
:::
::: {.fragment .fade-in fragment-index="1" style="position: absolute; width: 100%;"}
```{r out.width="150%", fig.show='hold', fig.align='center'}
knitr::include_graphics("tournament_comparison_plot_close.png")
```
:::
::::::

### 2025-10-22 mutual_information_curves.qmd
Updates

windowsFonts(Arial = windowsFont("Arial"))
comparison_plot <- ggplot(df_long, aes(x = indices, y = MI, color = Method, group = Method)) +
geom_line(linewidth = 2.5) +           # Add lines
geom_point(size=3) +          # Add points
labs(
title = "Comparison of Tournament Structures with Normal Strengths",
x = "Top i Number of Teams",
y = "Normalized Mutual Information \\ Entropy"
) +
theme_minimal() +       # Use a clean theme
theme(text = element_text(family = "Arial", size = 32),
  legend.position = "bottom",
  legend.box = "vertical",
  plot.title = element_text(hjust = 0.5, size = 36),
  axis.title = element_text(size = 30),
  axis.text = element_text(size=30)) +
  guides(color = guide_legend(nrow = 5)) +
  scale_color_manual(values = method_colors)
ggsave(
  filename = "tournament_comparison_plot.png",  # Change file type if needed
  plot = comparison_plot,  # Saves the last ggplot created
  dpi = 600,        
  bg = "white",
  units = "in",
  width = 15.28,
  height = 13.43
)

>>>>

windowsFonts(Arial = windowsFont("Arial"))
ggplot(df_long, aes(x = indices, y = MI, color = Method, group = Method)) +
geom_line(linewidth = 2.5) +           # Add lines
geom_point(size=3) +          # Add points
labs(
title = "Comparison of Tournament Structures with Normal Strengths",
x = "Top i Number of Teams",
y = "Normalized Mutual Information \\ Entropy"
) +
theme_minimal() +       # Use a clean theme
theme(text = element_text(family = "Arial", size = 32),
  legend.position = "bottom",
  legend.box = "vertical",
  plot.title = element_text(hjust = 0.5, size = 36),
  axis.title = element_text(size = 30),
  axis.text = element_text(size=30)) +
  guides(color = guide_legend(nrow = 5)) +
  scale_color_manual(values = method_colors)
ggsave(
  filename = "tournament_comparison_plot.png",  # Change file type if needed
  plot = last_plot(),  # Saves the last ggplot created
  dpi = 600,        
  bg = "white",
  units = "in",
  width = 15.28,
  height = 13.43
)
